Community Embeddings for Friend Suggestions

### 2020-10-12 paper-ffs.tex
oh yea, citet, then ok
https://tex.stackexchange.com/questions/202963/how-to-cite-author-in-ieee-format

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.48\textwidth]{images/fb/graph_d4.png}
    \caption{Social circles Facebook graph plotted with networkx's spring layout and node colors representing community membership obtained by ComE BGMM+VI with $D=4$ \cite{networkx}.}
    \label{fig:fb_graph}
\end{figure}

@@

The recommender system based on community embeddings with the Bayesian Gaussian mixture model and variational inference is quantitatively evaluated. Friend suggestions are generated for the Social circles Facebook dataset \cite{social_circles_fb, social_circles_in_ego_networks}.

The method of generating friend suggestions using ComE BGMM+VI embeddings and the smallest-distance approach is applied to the Social circles Facebook graph. Both Algorithm \ref{alg:friend_sug} and Algorithm \ref{alg:friend_sug_com} are evaluated. The top-$N$ recommendations are evaluated by the hit-rate metric.

@@

The Social circles Facebook dataset was sourced from the profile and network data of ten ego-networks (egonets) through a custom Facebook app by \citeauthor{social_circles_in_ego_networks} as part of their \citeyear{social_circles_in_ego_networks} article \citet{social_circles_in_ego_networks}.\cite{social_circles_in_ego_networks}

@@

The Social circles Facebook graph is split into training and testing parts. For evaluation, the leave-one-out (LOO) method is used, where for each testing user one edge is left out, then if the left out edge is in the user's top-$N$ recommendations, a hit is counted, otherwise, a miss is recorded.
Users with only one connection are removed from the dataset since no network information is added by them.

$1169$ of the 4039 users of the Social circles Facebook graph have at least $50$ connections and are used for testing friend suggestions. The threshold of $50$ friends for considering users for testing is set to make sure enough data is available to make sensable suggestions for testing users.

@@

Community embeddings for the Social circles Facebook graph are generated by running ComE BGMM+VI with the hyperparameters listed in Table \ref{tab:params_fb}.

\begin{table}
    \centering
    \caption{Hyperparameters used for the Social circles Facebook dataset.}
    \label{tab:params_fb}
    \begin{tabular}{ l | c | r }
        parameter                    & notation & value       \\
        \hline
        \hline
        number\_walks                & $\gamma$ & $10$        \\
        \hline
        walk\_length                 & $\ell$   & $80$        \\
        \hline
        representation\_size         & $D$      & $2, 4, 128$ \\
        \hline
        num\_workers                 & \empty   & $10$        \\
        \hline
        num\_iter                    & \empty   & $3$         \\
        \hline
        com\_n\_init                 & \empty   & $10$        \\
        \hline
        reg\_covar                   & \empty   & $0.00001$   \\
        \hline
        batch\_size                  & \empty   & $50$        \\
        \hline
        window\_size                 & $\zeta$  & $10$        \\
        \hline
        negative                     & $m$      & $5$         \\
        \hline
        lr                           & \empty   & $0.025$     \\
        \hline
        alpha                        & $\alpha$ & $0.1$       \\
        \hline
        beta                         & $\beta$  & $0.1$       \\
        \hline
        down\_sampling               & \empty   & $0.0$       \\
        \hline
        communities                  & $K$      & $10$        \\
        \hline
        weight\_concentration\_prior & $\Gamma$ & $10^{-5}$   \\
    \end{tabular}
\end{table}

As is shown in Table \ref{tab:params_fb}, the embedding's representation size $D$ is varied along three values. A representation size $D \in [2,4,128]$ is chosen to determine the effect of the embedding's dimensionality on friend suggestions. It is hypothesized, that two dimensions are not sufficient to capture the structure of the Social circles Facebook graph, due to its size, therefore higher dimensional embeddings are evaluated as well.

@@

Fig. \ref{fig:fb_emb_anim_d2} shows node and community embeddings with representation size $D=2$. The limiting two-dimensional space does not allow ComE to represent the Social circles Facebook graph's structure sufficiently to utilize the $K=10$ components of the Gaussian mixture model. Only three components are used after the last of three iterations.

@@

    \caption{Hit-rates of Social circles Facebook graph's top-$N$ friend suggestions on $N$-axis for $D \in [2,4,128]$. Hit-rate lines for Algorithm \ref{alg:friend_sug} and Algorithm \ref{alg:friend_sug_com} overlap for $D=2$ and $D=4$.}
    \label{fig:fb_hit_rates}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \caption{Hit-rates of Social circles Facebook graph's top-$N$ friend suggestions for algorithms \ref{alg:friend_sug} and \ref{alg:friend_sug_com}, $N \in [10, 20]$, and $D \in [2,4,128]$.}
    \label{table:fb_hit_rates}
    \begin{tabular}{ l | l | c | c | c }
        \hline
        \empty                                              & \empty  & top-$5$         & top-$10$        & top-$20$        \\
        \hline
        \hline
        \multirow{3}{*}{Algorithm \ref{alg:friend_sug}}     & $D=2$   & 8.5\%           & 14.2\%          & 21.9\%          \\
                                                            & $D=4$   & 18.1\%          & 26.5\%          & 38.4\%          \\
                                                            & $D=128$ & \textbf{31.3\%} & \textbf{43.6\%} & \textbf{58.8\%} \\
        \hline
        \multirow{3}{*}{Algorithm \ref{alg:friend_sug_com}} & $D=2$   & 8.4\%           & 14.1\%          & 21.8\%          \\
                                                            & $D=4$   & 18.0\%          & 26.4\%          & 38.2\%          \\
                                                            & $D=128$ & \textbf{24.1\%} & \textbf{32.9\%} & \textbf{41.8\%} \\
        \hline
    \end{tabular}
\end{figure}

>>>>

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.48\textwidth]{images/fb/graph_d4.png}
    \caption{\citet{social_circles_fb} graph plotted with networkx's spring layout and node colors representing community membership obtained by ComE BGMM+VI with $D=4$ \cite{networkx}.}
    \label{fig:fb_graph}
\end{figure}

@@

The recommender system based on community embeddings with the Bayesian Gaussian mixture model and variational inference is quantitatively evaluated. Friend suggestions are generated for the \citet{social_circles_fb} dataset \cite{social_circles_fb, social_circles_in_ego_networks}.

The method of generating friend suggestions using ComE BGMM+VI embeddings and the smallest-distance approach is applied to the \citet{social_circles_fb} graph. Both Algorithm \ref{alg:friend_sug} and Algorithm \ref{alg:friend_sug_com} are evaluated. The top-$N$ recommendations are evaluated by the hit-rate metric.

@@

The \citet{social_circles_fb} dataset was sourced from the profile and network data of ten ego-networks (egonets) through a custom Facebook app by \citeauthor{social_circles_in_ego_networks} as part of their \citeyear{social_circles_in_ego_networks} article \citet{social_circles_in_ego_networks}.\cite{social_circles_in_ego_networks}

@@

The \citet{social_circles_fb} graph is split into training and testing parts. For evaluation, the leave-one-out (LOO) method is used, where for each testing user one edge is left out, then if the left out edge is in the user's top-$N$ recommendations, a hit is counted, otherwise, a miss is recorded.
Users with only one connection are removed from the dataset since no network information is added by them.

$1169$ of the 4039 users of the \citet{social_circles_fb} graph have at least $50$ connections and are used for testing friend suggestions. The threshold of $50$ friends for considering users for testing is set to make sure enough data is available to make sensable suggestions for testing users.

@@

Community embeddings for the \citet{social_circles_fb} graph are generated by running ComE BGMM+VI with the hyperparameters listed in Table \ref{tab:params_fb}.

\begin{table}
    \centering
    \caption{Hyperparameters used for the \citet{social_circles_fb} dataset.}
    \label{tab:params_fb}
    \begin{tabular}{ l | c | r }
        parameter                    & notation & value       \\
        \hline
        \hline
        number\_walks                & $\gamma$ & $10$        \\
        \hline
        walk\_length                 & $\ell$   & $80$        \\
        \hline
        representation\_size         & $D$      & $2, 4, 128$ \\
        \hline
        num\_workers                 & \empty   & $10$        \\
        \hline
        num\_iter                    & \empty   & $3$         \\
        \hline
        com\_n\_init                 & \empty   & $10$        \\
        \hline
        reg\_covar                   & \empty   & $0.00001$   \\
        \hline
        batch\_size                  & \empty   & $50$        \\
        \hline
        window\_size                 & $\zeta$  & $10$        \\
        \hline
        negative                     & $m$      & $5$         \\
        \hline
        lr                           & \empty   & $0.025$     \\
        \hline
        alpha                        & $\alpha$ & $0.1$       \\
        \hline
        beta                         & $\beta$  & $0.1$       \\
        \hline
        down\_sampling               & \empty   & $0.0$       \\
        \hline
        communities                  & $K$      & $10$        \\
        \hline
        weight\_concentration\_prior & $\Gamma$ & $10^{-5}$   \\
    \end{tabular}
\end{table}

As is shown in Table \ref{tab:params_fb}, the embedding's representation size $D$ is varied along three values. A representation size $D \in [2,4,128]$ is chosen to determine the effect of the embedding's dimensionality on friend suggestions. It is hypothesized, that two dimensions are not sufficient to capture the structure of the \citet{social_circles_fb} graph, due to its size, therefore higher dimensional embeddings are evaluated as well.

@@

Fig. \ref{fig:fb_emb_anim_d2} shows node and community embeddings with representation size $D=2$. The limiting two-dimensional space does not allow ComE to represent the \citet{social_circles_fb} graph's structure sufficiently to utilize the $K=10$ components of the Gaussian mixture model. Only three components are used after the last of three iterations.

@@

    \caption{Hit-rates of \citet{social_circles_fb} graph's top-$N$ friend suggestions on $N$-axis for $D \in [2,4,128]$. Hit-rate lines for Algorithm \ref{alg:friend_sug} and Algorithm \ref{alg:friend_sug_com} overlap for $D=2$ and $D=4$.}
    \label{fig:fb_hit_rates}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \caption{Hit-rates of \citet{social_circles_fb} graph's top-$N$ friend suggestions for algorithms \ref{alg:friend_sug} and \ref{alg:friend_sug_com}, $N \in [10, 20]$, and $D \in [2,4,128]$.}
    \label{table:fb_hit_rates}
    \begin{tabular}{ l | l | c | c | c }
        \hline
        \empty                                              & \empty  & top-$5$         & top-$10$        & top-$20$        \\
        \hline
        \hline
        \multirow{3}{*}{Algorithm \ref{alg:friend_sug}}     & $D=2$   & 8.5\%           & 14.2\%          & 21.9\%          \\
                                                            & $D=4$   & 18.1\%          & 26.5\%          & 38.4\%          \\
                                                            & $D=128$ & \textbf{31.3\%} & \textbf{43.6\%} & \textbf{58.8\%} \\
        \hline
        \multirow{3}{*}{Algorithm \ref{alg:friend_sug_com}} & $D=2$   & 8.4\%           & 14.1\%          & 21.8\%          \\
                                                            & $D=4$   & 18.0\%          & 26.4\%          & 38.2\%          \\
                                                            & $D=128$ & \textbf{24.1\%} & \textbf{32.9\%} & \textbf{41.8\%} \\
        \hline
    \end{tabular}
\end{figure}
